A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-11 evaluation.tex
Evaluation + kill your darlings
Fix numbers issues, new graph

We evaluate the performance of \Catra{} on~\NrBenchmarks{} instances of Parikh
automata intersection problems generated by the \OstrichPlus{} string constraint
solver when solving the PyEx benchmarks~\cite{pyex}. After generating an
initial~\InitialNrBenchmarks{},we remove~\NrTrivial{} instances solved in under
five seconds by baseline. We also attempted to benchmark instances generated by
\Ostrich{} solving the kaluza-len (\numprint{38227} instances) and pyex-len
(\numprint{791} instances) benchmark suites, but had to discard them since they
were all trivial. For instance, on a laptop, \Calculus{} could solve every
instance from kaluza-len in under five seconds, mean about 0.1s. The benchmarks
are run on commit~\texttt{\commit}.

The benchmarks are executed in parallel across a cluster of \Fudge{identical}
machines, \BenchmarkRig{}, but as the sole job for each machine.  We compiled
the code using Scala~\ScalaVersion{}, and executed the experiments
on~\JvmVersion{} with a maximum heap of~\MaxHeapSize{}. We used \Nuxmv{}
version~\NuxmvVersion{} invoked as a subprocess for each instance. Instances
were executed in batches of \BatchSize{}, each given a fresh JVM. Each JVM was
warmed up for \numprint{10}s on a random benchmark from the set before starting
to execute. We believe this represents a realistic use case where \Calculus{} is
used to support e.g a string solver. Experiments were executed in random order
for all backends. Each instance got a time budget of~\RuntimeTimeout.

@@

In \cref{fig:solve-division} we show how many of the~\NrBenchmarks{} instances
the respective back-end could solve. A summary of their outcomes by instance
type is also available in \cref{tab:solve-status}. Note that many instances lack
a corum ground truth as they are solved by only one backend. We see that
\Calculus{} generally outperforms \Nuxmv{} on determining unsatisfiability, as
does baseline while being similar at satisfiable instances. Both \Calculus{} and
baseline outperforms baseline on satisfiable instances. On satisfiable
instances, \Nuxmv and \Calculus{} has similar performance.

@@

>>>>

We evaluate the performance of \Catra{} on~\NrBenchmarks{} instances of Parikh
automata intersection problems generated by the \OstrichPlus{} string constraint
solver when solving the PyEx benchmarks~\cite{pyex}. After generating an
initial~\InitialNrBenchmarks{}, we remove~\NrTrivial{} instances solved in under
five seconds by baseline as well as~\NrInvalid{} instances that produced errors
during experimentation. We also attempted to benchmark instances generated by
\Ostrich{} solving the kaluza-len (\numprint{38227}~instances) and pyex-len
(\numprint{791}~instances) benchmark suites but discarded them since they were
all trivial. For instance, on a laptop, \Calculus{} could solve every instance
from kaluza-len in under five seconds (mean about 0.1s). The benchmarks are run
on commit~\texttt{\commit}.

The benchmarks are executed in parallel across a cluster of \Fudge{identical}
machines, \BenchmarkRig{}, but as the sole job for each machine.  We compiled
the code using Scala~\ScalaVersion{} and executed the experiments
on~\JvmVersion{} with a maximum heap of~\MaxHeapSize{}. We used \Nuxmv{}
version~\NuxmvVersion{} invoked as a subprocess for each instance. Instances
were executed in batches of \BatchSize{}, each given a fresh JVM. Each JVM was
warmed up for \numprint{10}s on a random benchmark from the set before starting
to execute. We believe this represents a realistic use case where \Calculus{} is
used to support, e.g., a string solver. Experiments were executed in random order
for all backends. Each instance got a time budget of~\RuntimeTimeout.

@@

In \cref{fig:solve-division}, we show how many of the~\NrBenchmarks{} instances
the respective back-end could solve. A summary of their outcomes by instance
type is also available in \cref{tab:solve-status}. Note that many instances lack
a corum ground truth as they are solved by only one backend. We see that
\Calculus{} generally outperforms \Nuxmv{} on determining unsatisfiability, as
does baseline while being similar at satisfiable instances. Both \Calculus{} and
baseline outperforms baseline on satisfiable instances. On satisfiable
instances, \Nuxmv and \Calculus{} has similar performance.

@@

We include this section to show that \Calculus{} can be used to enhance the
performance of an automaton-based string solver with cost-enriched automata like
\Ostrich{}. However, significant engineering effort remains to bring the
integration to a state where it can participate in the full SMT-COMP.
